% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{../res}
\usepackage{multicol}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Raphael Reyna}

\address{Email: raphaelreyna@protonmail.com \\
  Phone: (626) 384-1342\\
  Site: www.raphaelreyna.works}
                           
                        
\begin{resume} 
\section{PROJECTS}
  
\normalsize{\section{TinyTerm}}
A macOS app; a fire-and-forget terminal emulator that lives in the menu bar.
Uses the Darwin framework to maintain an active PTY session running a shell.
A shortcut brings up a dialog to enter commands to be ran.
\begin{itemize}
\item {\bf Languages Used: } Swift 4 
\item {\bf Technologies Used: } AppKit, Carthage, Darwin, Xcode
\end{itemize}

\normalsize{\section{Chapters}}
A macOS app for splitting PDFs into smaller PDFs.
Can split PDFs based on a user defined layout, or using the
table of contents of the PDF to split it into its chapters.
If a PDF is split based on its table of contents, the files are saved in a
structured directory that reflects the structure of the table of contents.
\begin{itemize}
\item{ \bf Languages Used: } Swift 4 
\item { \bf Technologies Used: } AppKit, Carthage, PDFKit, Xcode
\end{itemize}

\normalsize{\section{Subseries Plotter}}
A python app that uses GPGPU to render computationally expensive
fractals.
Uses OpenCL to compute the fractal data, and then OpenGL to plot the data.
OpenCL and OpenCL are used interoperably in order to minimize the performance hit due to context switching.
\begin{itemize}
\item {\bf Languages Used: } Python 3, OpenCL C, GLSL C
\item {\bf Technologies Used: } OpenGL, OpenCL
\end{itemize}

\normalsize{\section{LWP Splitter}}
Fully containerized application that generates and stores mathematical data for
research.
Uses PostgreSQL to not only store data but to efficiently prepare the data for
consumption by machine learning algorithms for training.
A python app generates the data and sends it to the PostgreSQL
database, while providing a REST API to control the data generation process.
\begin{itemize}
\item{ \bf Languages Used: } Python, PL/pgSQL, SQL, Bash, YAML
\item { \bf Technologies Used: } Flask, Flask-Restful, Numpy, Pillow, PostgreSQL, Docker
\end{itemize}

\section{RELEVANT EXPERIENCE}
{\bf Cal Poly Pomona, Pomona, CA}\newline
{\it Mathematics Instructor}\newline
{\bf 2015 - Present}\newline
Responsibilities included designing a course schedule, complete with lecture and
evaluation material; as well as leading the class through the material and
regularly conducting evaluations of student performance.\newline
Courses taught:
\begin{multicols}{2}
\begin{itemize}
\item Calculus I {\it and} Calculus II
\item Trigonometry
  \columnbreak
\item College Algebra
\item Remedial Mathematics
\end{itemize}
\end{multicols}

\section{EDUCATION}
Cal Poly Pomona, Pomona, CA \\
B.S. Applied Mathematics and Statistics with a minor in Physics, 2015 \newline
M.S. Pure Mathematics, expected summer 2019

  \section{RELEVANT SKILLS}
Bash, BSD, C, C++, Carthage, Clang, Cocoapods, Data Science, Docker, Emacs,
ES6, Flask, Forecasting,
Full stack web development, GCC, GDB, Git/Github, GPGPU, Gunicorn, iOS, Linux, LLDB,
macOS, Machine
Learning, Make, Mathematica, NodeJS, NPM, OpenCL, OpenGL, PostgreSQL,
PyPi, R/RStudio, RESTful APIs, SQL, UNIX, WebGL, Xcode,

  \section{OTHER}
  3D Printing, CAD, Circuit Design, Hardware Design, Italian, Soldering, Spanish
 
\end{resume}
\end{document}
