% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{multicol}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Raphael Reyna}

\address{ raphaelreyna@protonmail.com \\
  (626) 384-1342 }
                           
                        
\begin{resume}
\section{EDUCATION}
Cal Poly Pomona, Pomona, CA \\
B.S. Applied Mathematics and Statistics with a minor in Physics, 2015 \newline
M.S. Pure Mathematics, expected summer 2019
 
\section{PROJECTS}
  
\normalsize{\section{Subseries Web App}}
A client side web app to assist in
research in number theory (written as a part of my Master's thesis on subseries
of holomorphic functions). Constructs, evaluates and plots millions of complex
valued functions in parallel. Utilized WebGL for general computing on the GPU.
Utilized HTML5's {\it canvas} to create dynamic controls.
\begin{itemize}
\item {\bf Languages Used: } HTML, Javascript, CSS
\item {\bf Platforms/Frameworks Used: } WebGL, HTML canvas API, Math.js
\end{itemize}

\normalsize{\section{BBMail}} Server application that enables teachers to use
the Blackboard learning management system via email, avoiding the web interface.
Works by monitoring email accounts, acting only on emails from the user.
Interfaces with Blackboard's website using selenium to drive a headless Chrome
browser.
\begin{itemize}
\item {\bf Languages Used: } Python
\item {\bf Libraries/Frameworks Used: } Selenium, Beautiful Soup 4, Python
  Standard Library
\end{itemize}

\normalsize{\section{Wine Quality}}
A report on the analysis of various machine learning models to determine wine
quality based on physical data.
Involved designing and fitting various statistical models to wine data, and
evaluating their performance in predicting wine quality.
\begin{itemize}
\item {\bf Languages Used: } R, LaTeX
\item {\bf Technologies Used: } RStudio
\end{itemize}

\normalsize{\section{TinyTerm}} A macOS app; a small terminal emulator that
lives in the menu bar. Uses the Darwin libraries to open a pseudo-terminal
device file to maintain an interactive shell session going.
\begin{itemize}
\item {\bf Languages Used: } Swift 4
\item {\bf Frameworks Used: } Darwin, Foundation, Cocoa
\end{itemize}

\section{RELEVANT EXPERIENCE}
{\bf Cal Poly Pomona, Pomona, CA}\newline
{\it Mathematics Instructor}\newline
{\bf 2015 - Present}\newline
Responsibilities included designing a course schedule, complete with lecture and
evaluation material; as well as leading the class through the material and
regularly conducting evaluations of student performance.\newline
Courses taught:
\begin{multicols}{2}
\begin{itemize}
\item Calculus I {\it and} Calculus II
\item Trigonometry
  \columnbreak
\item College Algebra
\item Remedial Mathematics
\end{itemize}
\end{multicols}

  \section{RELEVANT SKILLS}
  Linux, BSD, *Nix, macOS, Bash, Git/Github, Version Control, NPM, NodeJS, ES6, PyPi, Pip, Continuous Integration,
  Full Stack Development, Responsive Web Design, Data Science, Machine Learning Algorithms, Time Series, Forecasting,
  GPGPU, OpenCL, OpenGL, C, C++, Make, GCC, clang, GDB, LLDB, XCode, Carthage,
  CocoaPods, Mathematica, R/RStudio, Emacs, Nginx, Gunicorn, Flask, REST API, Arduino, PID control

  \section{OTHER}
  Spanish, Italian, Portuguese, 3D Printing, CAD, 3D Modeling, Circuit Design,
  Hardware Design, Soldering 
 
\end{resume}
\end{document}
