% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{../res}
\usepackage{multicol}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Raphael Reyna}

\address{Email: raphaelreyna@protonmail.com \\
  Phone: (626) 384-1342\\
  Site: www.raphaelreyna.works}
                           
                        
\begin{resume} 
\section{PROJECTS}
  
\normalsize{\section{Subseries Web App}}
A purely client side application written in vanilla JS.
Uses WebGL to compute and render computationally expensive fractals in real time.
\begin{itemize}
\item {\bf Languages Used: } HTML, Javascript, CSS
\item {\bf Technologies Used: } HTML 5 canvas' WebGL and 2D contexts
\end{itemize}

\normalsize{\section{LWP Splitter}}
Fully containerized backend to a web app for studying Littlewood polynomials;
generates and stores mathematical data in a PostgresSQL database.
Provides a RESTful API for controlling the data generation process.
Can also produce plots of SQL queries, as well as generate labeled training data for
machine learning.
\begin{itemize}
\item{ \bf Languages Used: } Python, PL/pgSQL, SQL, Bash, YAML
\item { \bf Technologies Used: } Flask, Flask-Restful, Numpy, Pillow, PostgreSQL, Docker
\end{itemize}

\normalsize{\section{Online Portfolio}}
A static website that serves as an online resume.
Features custom animations using both the HTML 5 canvas 2D context and SVG.
\begin{itemize}
\item{ \bf Languages Used: } HTML 5, Javascript, CSS
\item{ \bf Technologies Used: } HTML 5 canvas 2D context, SVG, Materialize CSS
\end{itemize}

\normalsize{\section{BBMail}} Server application that enables teachers to use
the Blackboard learning management system via email, avoiding the web interface.
Works by monitoring email accounts, acting only on emails from the user.
Interfaces with Blackboard's website using selenium to drive a headless Chrome
browser.
\begin{itemize}
\item {\bf Languages Used: } Python
\item {\bf Technologies Used: } Selenium, Beautiful Soup 4, Python
  Standard Library
\end{itemize}

\section{RELEVANT EXPERIENCE}
{\bf Cal Poly Pomona, Pomona, CA}\newline
{\it Mathematics Instructor}\newline
{\bf 2015 - Present}\newline
Responsibilities included designing a course schedule, complete with lecture and
evaluation material; as well as leading the class through the material and
regularly conducting evaluations of student performance.\newline
Courses taught:
\begin{multicols}{2}
\begin{itemize}
\item Calculus I {\it and} Calculus II
\item Trigonometry
  \columnbreak
\item College Algebra
\item Remedial Mathematics
\end{itemize}
\end{multicols}

\section{EDUCATION}
Cal Poly Pomona, Pomona, CA \\
B.S. Applied Mathematics and Statistics with a minor in Physics, 2015 \newline
M.S. Pure Mathematics, expected summer 2019

  \section{RELEVANT SKILLS}
*Nix, Arduino, Bash, BSD, C, C++, Carthage, Clang, Cocoapods, Data Science, Docker, Emacs,
ES6, Flask, Forecasting,
Full stack web development, GCC, GDB, Git/Github, GPGPU, Gunicorn, iOS, Linux, LLDB,
macOS, Machine
Learning, Make, Mathematica, Nginx, NodeJS, NPM, OpenCL, OpenGL, PID, Pip, PostgreSQL,
PyPi, R/RStudio, Responsive web design, RESTful APIs, SQL, Time Series, UNIX, WebGL, Xcode,

  \section{OTHER}
  3D Printing, CAD, Circuit Design,
  Hardware Design, Italian, Soldering, Spanish
 
\end{resume}
\end{document}
