% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{../res}
\usepackage{multicol}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Raphael Reyna}

\address{Email: raphaelreyna@protonmail.com \\
  Phone: (626) 384-1342 \\
  Site: www.raphaelreyna.works}
                           
                        
\begin{resume} 
\section{PROJECTS}
  
\normalsize{\section{Subseries Web App}}
A purely client side application written in vanilla JS with custom ReactJS components.
Utilizes both of HTML 5's Canvas contexts, WebGL and 2D, to compute and render computationally expensive fractals in real
time.
\begin{multicols}{2}
\begin{itemize}
\item {\bf Languages Used: }\newline HTML, Javascript, CSS
  \columnbreak
\item {\bf Platforms/Frameworks Used: }\newline WebGL, HTML canvas API, Math.js
\end{itemize}
\end{multicols}

\normalsize{\section{LWP Splitter}}
Containerized backend to a web app for studying polynomials roots;
generates and stores mathematical data in a database.
Provides a RESTful API for controlling the data generation process.
Can produce plots of SQL queries, as well as generate labeled training data for machine learning.
\begin{multicols}{2}
\begin{itemize}
\item {\bf Languages Used: }\newline
  Python, PL/pgSQL, SQL, Bash, YAML
  \columnbreak
\item {\bf Technologies Used: } \newline
  Flask, Flask-Restful, Numpy, Pillow, PostgreSQL, Docker
\end{itemize}
\end{multicols}

\normalsize{\section{Wine Quality}}
A report on the analysis of various machine learning models to determine wine
quality based on physical data.
Involved designing and fitting various statistical machine learning models to wine data, and
evaluating their performance in predicting wine quality.
\begin{itemize}
\item {\bf Languages Used: }\newline R, LaTeX
\end{itemize}

\normalsize{\section{TinyTerm}} A macOS app; a small terminal emulator that
lives in the menu bar.
\begin{multicols}{2}
\begin{itemize}
\item {\bf Languages Used: } \newline Swift 4
  \columnbreak
\item {\bf Technologies Used: } \newline Darwin, Foundation, Cocoa
\end{itemize}
\end{multicols}

\section{RELEVANT EXPERIENCE}
{\bf Cal Poly Pomona, Pomona, CA}\newline
{\it Mathematics Instructor}\newline
{\bf 2015 - Present}\newline
Responsibilities included designing a course schedule, complete with lecture and
evaluation material; as well as leading the class through the material and
regularly conducting evaluations of student performance.\newline
\ \newline
Courses taught include: Calculus I, Calculus II, Trigonometry, College Algebra,
Remedial Mathematics.

\section{EDUCATION}
Cal Poly Pomona, Pomona, CA \\
B.S. Applied Mathematics and Statistics with a minor in Physics, 2015 \newline
M.S. Pure Mathematics, expected summer 2019

\section{RELEVANT SKILLS}
*Nix, Arduino, Bash, BSD, C, C++, Carthage, Clang, Cocoapods, Data Science, Docker, Emacs,
ES6, Flask, Forecasting,
Full stack web development, GCC, GDB, Git/Github, GPGPU, Gunicorn, iOS, Linux, LLDB,
macOS, Machine
Learning, Make, Mathematica, Nginx, NodeJS, NPM, OpenCL, OpenGL, PID, Pip, PostgreSQL,
PyPi, R/RStudio, ReactJS, Responsive web design, RESTful APIs, SQL, Time Series, UNIX, WebGL, Xcode,

  \section{OTHER}
  3D Printing, CAD, Circuit Design,
  Hardware Design, Italian, Soldering, Spanish
 
\end{resume}
\end{document}
